---
title: "Plots"
author: "Lasse Hansen"
output: html_document
---

# Setup
```{r setup}
pacman::p_load(tidyverse, RColorBrewer, patchwork,
               colorspace, scico, pROC, ggpmisc, 
               knitr, kableExtra, brms, broom, broom.mixed, 
               tidybayes, bayesplot, here, glue)


# make directories
make_dir <- function(dir){
  if (!dir.exists(dir)){
    dir.create(dir)
  }
}
dirs = c(here("figs"), here("supplementary"))
map(dirs, make_dir)

# Read MFCC data
df <- read.csv("data/publication_data.csv")

# Read MFCC data with column indicating whether speaker diarization/segmentation has taken place
seg_df <- read_csv('data/seg_no_seg.csv') %>% 
  mutate(Diagnosis_visit =  Diagnosis_only,
         Diagnosis_only = str_sub(Diagnosis_only,end=-2),
         visit = str_sub(Diagnosis_visit, start = -1)) %>% 
  # dc19 and dc15 are the same person, removing one
  # dp41 is only in the remission data (no audio from visit 1)
  filter(id_full != 'dc19', id_full != 'dp41') %>% 
  mutate(Diagnosis_rem = case_when(
    as.character(Diagnosis_visit) == "Depression1" ~ "Depression\n(First visit)",
    as.character(Diagnosis_visit) == "Depression2" ~ "Depression\n(Second visit)",
    as.character(Diagnosis_visit) == "Controls1" ~ "Controls\n(First visit)",
    as.character(Diagnosis_visit) == "Controls2" ~ "Controls\n(Second visit)",
    )
  )


# Set large text size for publication plots
theme_set(theme_minimal(base_size = 18))

# Set color palettes
d_v_pal <- darken(RColorBrewer::brewer.pal(6, 'Paired'), 0.2)[c(1,2,5,6)]
rem_pal <- d_v_pal
rem_pal[4] <- "#34BF39"

# Mute annoying summarise message
options(dplyr.summarise.inform=F)
# Set number of parallel MCMC cores

options(mc.cores = parallel::detectCores())

# function to convert probabilities back to log odds space
prob_to_log_odds <- function(prob) log(prob / (1 - prob))

# Filtered datasets only including the clean data (no background noise) and 30 second time bins or no windowing
wdf_30 <- df %>% 
  filter(clean == 'clean', window_size == '30') %>% 
  mutate(log_odds = prob_to_log_odds(probs)) 
  

wdf_full <- df %>% 
  filter(clean == 'clean', window_size == 'full')
```


# Main Manuscript
## Table 1 - Clinical Information
```{r table_1}
###### 
#This requires a dataset with more data on the participants and can therefore not be directly reproduced
######
# 
# library(table1)
# 
# wdf_full <- wdf_full %>% 
#   mutate(HamD_17 = ifelse(visit == 1, HamD17_Before, HamD17_After))
# 
# wdf_full$Gender <- factor(wdf_full$Gender, levels=c("f", "m"), labels=c("Female", "Male"))
# wdf_full$visit <- factor(wdf_full$visit, levels=c("1", "2"), labels=c("Visit 1", "Visit 2"))
# 
# 
# label(wdf_full$Gender) <- "Gender"
# label(wdf_full$Education) <- "Education (years)"
# label(wdf_full$HamD_17) <- "HamD-17"
# label(wdf_full$WorkingMemory) <- "Working Memory (OTS)"
# label(wdf_full$VerbalMemory) <- "Verbal Memory (HVLT-R)"
# label(wdf_full$SustainedAttention) <- "Sustained Attention (RVP)"
# 
# table1(~ Age + Gender  + Education + HamD_17 + WorkingMemory + VerbalMemory + SustainedAttention
#        | visit * Diagnosis_only, 
#        data=wdf_full,
#        overall=FALSE,
#        # footnote=c(
#        # "HamD-17 = Hamilton Depression Rating Scale (17-item version).",
#        # "Working Memory (OTS) = One Touch Stockings of Cambridge test.",
#        # "Verbal Memory (HVLT-R) = Hopkins Verbal Learning Test–Revised.",
#        # "Sustained Attention (RVP) = Rapid Visual Information Processing test.")
# )


```


## Figure 1 - Distribution of predictions, theta, and posterior from mixture model
### Figure 1a
```{r fig1_a}
fig1_a <- wdf_30 %>%
  mutate(visit = as.factor(visit)) %>%
  group_by(Diagnosis_rem, id_full) %>% 
  summarise(probs = mean(probs)) %>%
  group_by(Diagnosis_rem) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  mutate(Diagnosis_rem = paste0(Diagnosis_rem,'\nN = ',n)) %>% 
  
  ggplot(aes(Diagnosis_rem, probs, fill=Diagnosis_rem, color=Diagnosis_rem)) +
    geom_point(alpha=0.5, position = position_jitterdodge(jitter.width = 0.1)) +
    geom_boxplot(aes(group=Diagnosis_rem), alpha=0.3, width = 0.5, color='black') +
    ylim(0,1) +
    theme(legend.position = 'none',
          axis.title.x = element_blank(),
          axis.text.x = element_blank()) +
    scale_color_manual(values=rem_pal) +
    scale_fill_manual(values=rem_pal) +
    labs(y = "P(Happy)")
```

### Fig 1b
```{r fig1_b}
# Load model. See `model.Rmd` for model building.
mix_m <- readRDS(here("models", "mixture_model_sdprior_3_1.rds"))
# Extract mixing factors
ppm <- pp_mixture(mix_m)
# Extract mixing factor for group 1 (the other is just 1- that) 
wdf_30$theta_1 <-  ppm[, 1,][,1]
wdf_30$theta_2 <- 1 - wdf_30$theta_1 



# mean theta2 by id and group (for consistency with whats positive and negative)
fig1_b <- wdf_30 %>% 
  group_by(Diagnosis_rem, id_full) %>% 
  summarise(mean_theta = mean(theta_2)) %>% 
  ggplot(aes(mean_theta, Diagnosis_rem, fill=Diagnosis_rem, color=Diagnosis_rem)) +
  stat_dots(size=2, alpha=1) +
  scale_fill_manual(values = rem_pal) + 
  scale_color_manual(values = rem_pal) + 
  labs(x = expression(theta)) +
  theme(legend.position="none",
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
```

### Figure 1c
```{r fig1_c}
n_samples <-  4000

preprocess_samples <- function(df){
  # Add visit column
  samps_preproc <- df %>% 
    as_tibble() %>% 
    rename(Depression = V1, Remission = V2, Controls1 = V3, Controls2 = V4) %>%  
    gather() %>% 
    mutate(visit = c(rep("Visit 1", 2*n_samples), 
                     rep("Visit 2", 2*n_samples), 
                     rep("Visit 1", 2*n_samples), 
                     rep("Visit 2", 2*n_samples)))
  return(samps_preproc)
}

dummy_df <- tribble(~Diagnosis_only, ~visit,
                    "Depression", 0,
                    "Depression", 1,
                    "Controls", 0,
                    "Controls", 1)

samps_mix <- predict(mix_m, dummy_df, re_formula = NA, transform = inv_logit_scaled)
samps_raw_mix <- predict(mix_m, dummy_df, re_formula = NA, transform = inv_logit_scaled, summary=F) 


fig1_c <- samps_raw_mix %>% 
  preprocess_samples(.) %>% 
   mutate(key = case_when(
    as.character(key) == "Depression" ~ "\nDepression\n(First visit)\nN = 40\n",
    as.character(key) == "Remission" ~ "\nDepression\n(Second visit)\nN = 25\n",
    as.character(key) == "Controls1" ~ "\nControls\n(First visit)\nN = 42\n",
    as.character(key) == "Controls2" ~ "\nControls\n(Second visit)\nN = 25\n"
  )
  ) %>% 
ggplot(aes(value, visit, color = key, fill = key)) +
  stat_pointinterval(position=position_dodge(0.1), alpha=0.5, justification=0.4) + 
  stat_slab(alpha=0.5) + 
  coord_cartesian(xlim=c(0, 1)) +
  scale_color_manual(values = rem_pal) +
  scale_fill_manual(values = rem_pal) +
  labs(x = "P(Happy)") + 
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.title.y = element_blank(),
        legend.text.align = 0.5,
        legend.spacing.x = unit(0.5, 'cm')) 

# Row ordering: dep, rem, cont1, cont2
samps_mix
```


### Fig1 combined
```{r fig1}
(fig1_a | fig1_b) / (fig1_c ) +
  plot_annotation(tag_levels = "A") 

fig1_c <- fig1_c + guides(fill=guide_legend(ncol=2),
                          color=guide_legend(ncol=2))
fig1_a + fig1_b + fig1_c + guide_area() + 
  plot_layout(guides = "collect") + 
  plot_annotation(tag_levels = "A")

ggsave("figs/fig1.pdf", dpi="retina", width = 10, height = 8)
```

## Figure 2 - ROC and heatmap
### Fig2a
```{r fig2a}
roc_pal <- c("#d18975", "#8fd175")

make_roc_plot <- function(df, clean){

  roc_df_30 <- df %>% 
    filter(visit == 1, window_size == '30', clean == !!clean) 

  roc_df_full <- df %>% 
    filter(visit == 1, window_size == '30', clean == !!clean) %>% 
    group_by(id_full, Diagnosis_only) %>% 
    summarise(probs = mean(probs))
  
  roc_30 <- roc(roc_df_30$Diagnosis_only, roc_df_30$probs)
  roc_full <- roc(roc_df_full$Diagnosis_only, roc_df_full$probs)
  
  auc_30 <- auc(roc_30)[1]
  auc_full <- auc(roc_full)[1]
  
  thres_df <- pROC::coords(roc_30, 'best', transpose = F, ret=c("specificity", "sensitivity", "precision")) %>% 
    bind_rows(pROC::coords(roc_full, "best", transpose = F, ret=c("specificity", "sensitivity", "precision"))) %>% 
    mutate(AUC = c(auc_30, auc_full),
           across(where(is.numeric), round, 2),
           Type = c("Windows", "Summary")) %>% 
    relocate(Type, AUC) %>% 
    rename(Specificity = specificity, Sensitivity = sensitivity, Precision = precision, )
  
  
  p <- ggroc(list(Windows = roc_30, Summary = roc_full), legacy.axes = T) +
    xlab("FPR") + ylab("TPR") +
    scale_color_manual(values = roc_pal) +
    geom_segment(aes(x = 0, xend = 1, y = 0, yend = 1), color="darkgrey", linetype="dashed") +
    #annotate(geom = 'table', x = 0.08, y = 0.2, label = list(thres_df), vjust = 1, hjust = 0, alpha=0.5) +
    geom_table(data=thres_df, aes(x=0.08, y=0.2, label=list(thres_df)), 
               vjust =1, hjust=0) +
    theme(legend.title = element_blank(),
          legend.position = 'bottom')+
    coord_fixed()

  return(p)
}

fig2_a <- make_roc_plot(df, "clean")
```

### Fig2b
```{r fig2b}
wdf_30_v1 <- wdf_30 %>% 
  filter(visit==1) %>% 
  mutate(Diagnosis_rem = case_when(
    Diagnosis_rem == "Controls\n(First visit)" ~ "Controls\n(First visit)\nN = 42",
    Diagnosis_rem == "Depression\n(First visit)" ~ "Depression\n(First visit)\nN = 40",
  ))

fig2_b <- wdf_30_v1 %>% 
  group_by(id_full) %>% 
  # Add column with 'time' based on number of windows
  mutate(consec = sequence(rle(as.character(id_full))$lengths)) %>% 
  ungroup() %>%
  group_by(Diagnosis_rem) %>% 
  mutate(id_full = fct_reorder(id_full, probs, .fun = median, .desc=TRUE)) %>% 
  ggplot(aes(consec-1, id_full, fill=probs)) +
  geom_tile() +
  facet_wrap(~Diagnosis_rem, scales='free_y') +
  scale_fill_scico(palette = 'lajolla', direction = -1) +
  labs(x = 'Time (30 sec windows)', y = "ID", fill='P(Happy)') +
  theme(axis.text.y = element_blank(),
        legend.position = "bottom")

```

### Figure 2 combined
```{r fig2}
fig2_a + fig2_b + plot_annotation(tag_levels = "A")

ggsave("figs/fig2.pdf", dpi="retina", width = 10, height = 8)
```

## Figure 3 - Preprocessing analysis
### fig3 a
```{r fig3_a}
ns = wdf_30 %>% 
  group_by(Diagnosis_rem, id_full) %>% 
  tally() %>% 
  group_by(Diagnosis_rem) %>% 
  tally()

denoise <- df %>% 
  filter(window_size=='30') %>% 
  group_by(Diagnosis_rem, id_full, clean) %>% 
  summarise(probs = mean(probs)) %>% 
  mutate(preproc = ifelse(clean == "clean", "Diarized", "Raw")) %>% 
  select(Diagnosis_rem, id_full, probs, preproc)

fig3_a <- seg_df %>% 
  filter(segmented == FALSE) %>% 
  group_by(Diagnosis_rem, id_full) %>% 
  summarise(probs = mean(probs)) %>% 
  mutate(preproc = "Not diarized") %>% 
  bind_rows(denoise) %>% 
  left_join(ns, by="Diagnosis_rem") %>% 
  mutate(Diagnosis_rem = paste0(Diagnosis_rem,'\nN = ',n),
         preproc = fct_rev(as.factor(preproc))) %>% 
  ggplot(aes(Diagnosis_rem, probs, fill = preproc)) +
    geom_boxplot(width=.5, alpha=0.5, color='black') +
    scale_fill_brewer(palette = "Dark2", direction=-1) +
    ylim(0, 1) +
    labs(y = 'P(Happy)') +
    theme(axis.title.x = element_blank(),
          legend.title = element_blank(),
          legend.position="bottom")
```

### fig3 b preprocessing
```{r fig3_b_preproc}

get_auc <- function(df, clean, seg_df=F, return_roc_obj=F){
  
  if(seg_df){
    roc_df_30 <- df %>% 
      filter(visit == 1, window_size == '30', segmented == F)
    
    roc_df_full <- df %>% 
      filter(visit == 1, window_size == '30', segmented == F) %>% 
      group_by(id_full, Diagnosis_only) %>% 
      summarise(probs = mean(probs))
  }
  else{
    roc_df_30 <- df %>% 
      filter(visit == 1, window_size == '30', clean == !!clean) 
    
    roc_df_full <- df %>% 
      filter(visit == 1, window_size == '30', clean == !!clean) %>% 
      group_by(id_full, Diagnosis_only) %>% 
      summarise(probs = mean(probs))
  }
  
  roc_30 <- roc(roc_df_30$Diagnosis_only, roc_df_30$probs)
  ci_low_30 <- round(ci.auc(roc_30)[1], 2)
  ci_high_30 <- round(ci.auc(roc_30)[3], 2)
  roc_full <- roc(roc_df_full$Diagnosis_only, roc_df_full$probs)
  ci_low_full <- round(ci.auc(roc_full)[1], 2)
  ci_high_full <- round(ci.auc(roc_full)[3], 2)
  
  auc_30 <- auc(roc_30)[1]
  auc_full <- auc(roc_full)[1]
  
  thres_df <- pROC::coords(roc_30, 
                           'best', 
                           transpose = F, 
                           ret=c("threshold", "specificity", 
                                 "sensitivity", "precision")) %>% 
    bind_rows(pROC::coords(roc_full, 
                           "best", 
                           transpose = F, 
                           ret=c("threshold", "specificity", 
                                 "sensitivity", "precision"))) %>% 
    mutate(AUC = c(auc_30, auc_full),
           `AUC CI` = c(paste(ci_low_30, ci_high_30, sep="-"), 
                        paste(ci_low_full, ci_high_full, sep="-")),
           across(where(is.numeric), round, 2),
           Type = c("Windows", "Summary")) %>% 
    relocate(Type, AUC, `AUC CI`) %>% 
    rename(Threshold = threshold, Specificity = specificity, 
           Sensitivity = sensitivity, Precision = precision) %>% 
    as_tibble()
  
  if(clean != "null"){
    thres_df <- thres_df %>% 
      mutate(Data = clean)
  }
  else{
    thres_df <- thres_df %>% 
      mutate(Data = "seg")
  }
  
  if(return_roc_obj){
    return(list("30" = roc_30, "full" = roc_full))
  }
  else{
    return(thres_df)
  }
}

### move to S part
clean_auc <- get_auc(df, "clean")
raw_auc <- get_auc(df, "raw")
seg_auc <- get_auc(seg_df, "null", T)

bind_rows(clean_auc, raw_auc, seg_auc) %>% 
  relocate(Data) %>% 
  arrange(Type, desc(AUC)) %>% 
  select(-Type) %>% 
  mutate(Data= recode(Data, clean = "Diarized", raw = "Raw", seg = "Not diarized")) %>% 
  kbl() %>% 
  kable_classic(full_width = F) %>% 
  pack_rows("Summary", 1, 3) %>% 
  pack_rows("Windows", 4, 6)
```
### fig3 b
```{r}
clean_rocs <- get_auc(df, "clean", return_roc_obj = T)
raw_rocs <- get_auc(df, "raw", return_roc_obj = T)
seg_rocs <- get_auc(seg_df, "null", T, return_roc_obj = T)

fig3_b <- ggroc(list(`Raw` = raw_rocs$`30`,
           `Not diarized` = seg_rocs$`30`,
           `Diarized` = clean_rocs$`30`),
      legacy.axes = T) +
  xlab("FPR") + ylab("TPR") +
  scale_color_brewer(palette = 'Dark2', direction = -1) +
  geom_segment(aes(x = 0, xend = 1, y = 0, yend = 1), color="darkgrey", linetype="dashed") +
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  coord_fixed()
```

### fig3 c
```{r fig3_c}
# Fit roc on window basis
fit_roc <- function(df) roc(df$Diagnosis_only, df$probs)
# Fit roc summarised by id
fit_roc_summarized <- function(df){
  df <- df %>% 
    group_by(id_full, Diagnosis_only) %>% 
    summarise(probs = mean(probs))
  return(fit_roc(df))
}
extract_auc_ci <- function(roc_fit){
  auc_ci <- ci(roc_fit)
  return(data.frame(auc_low = auc_ci[1], auc = auc_ci[2], auc_high = auc_ci[3]))
} 


clean_v1_df <- df %>% 
  filter(clean == "clean", visit == 1) %>% 
  group_by(window_size) %>% 
  nest()

rocs_window <- clean_v1_df %>% 
  mutate(roc_fit = map(data, fit_roc)) %>% 
  mutate(aucs = map(roc_fit, extract_auc_ci),
         summarised = F) 

rocs_summarized <- clean_v1_df %>% 
  mutate(roc_fit = map(data, fit_roc_summarized)) %>% 
  mutate(aucs = map(roc_fit, extract_auc_ci),
         summarised = T) 

level_order <- c('2', '5', '10', '15', '20', '25', '30', 'full')

fig3_c <- rocs_window %>% 
  unnest(aucs) %>%
  ggplot(aes(factor(window_size, level = level_order), auc, color = summarised)) +
  geom_point() +
  geom_errorbar(aes(ymin = auc_low, ymax = auc_high), width = 0.5) +
  scale_color_manual(values = c("#56B4E9")) +
  labs(x = "Window size (seconds)", y = "AUC", color = "Summarized") +
  theme(legend.position="none")

```
### Figure 3 combined
```{r fig3}
fig3_a / (fig3_b | fig3_c) + plot_annotation(tag_levels = "A") 

ggsave("figs/fig3.pdf", dpi="retina", width = 10, height = 8)
```


# In-text numbers
## Mixture-model
```{r}
# model summary
mix_m

# extract means of the mixtures and estimated theta for each diagnostic group
tidy(mix_m, parameters = "^b") %>% 
  mutate(across(where(is.numeric), ~ inv_logit_scaled(.x)))

# calculate standard deviation of the two mixtures
params <- tidy(mix_m, parameters = "^b_mu|^sigma")

mu1 <- as.numeric(params[params$term == "b_mu1_(Intercept)", "estimate"])
mu2 <- as.numeric(params[params$term == "b_mu2_(Intercept)", "estimate"])

sigma1 <- as.numeric(params[params$term == "sigma1", "estimate"])
sigma2 <- as.numeric(params[params$term == "sigma2", "estimate"])

sigma1_low <- inv_logit_scaled(mu1 - sigma1)
sigma1_high <- inv_logit_scaled(mu1 + sigma1)
sigma2_low <- inv_logit_scaled(mu2 - sigma2)
sigma2_high <- inv_logit_scaled(mu2 + sigma2)

mu1_probs <- inv_logit_scaled(mu1)
mu2_probs <- inv_logit_scaled(mu2)

# sigma 1
sigma1_low <- mu1_probs - sigma1_low
sigma1_high <- sigma1_high - mu1_probs

# not symmetric due to the non-linearities therefore taking the mean
mean(c(sigma1_low, sigma1_high))
# sigma 2
sigma2_low <- mu2_probs - sigma2_low
sigma2_high <- sigma2_high - mu2_probs

mean(c(sigma2_low, sigma2_high))
```

## Number of correct predictions with optimal cut-off
```{r}
cutoff_preds <- wdf_30 %>% 
  group_by(Diagnosis_visit, id_full) %>% 
  summarize(probs = mean(probs)) %>% 
  mutate(pred = if_else(probs > 0.3831379, 1, 0))  

cutoff_preds %>% 
  group_by(Diagnosis_visit) %>% 
  summarise(sum_pred_control = sum(pred), n = n()) %>% 
  mutate(percent_pred_control = sum_pred_control / n * 100)
# Number/percent of participants predicted as controls
```


# Supplementary Materials
## Table S1 - Interview length
```{r descriptive stats}
# Table

seg_dur <- wdf_30 %>% 
  group_by(Diagnosis_only, visit, id_full) %>% 
  summarize(n_windows = n()) %>% 
  group_by(Diagnosis_only, visit) %>% 
  summarize(mean_duration = mean(n_windows)/2, sd_duration = sd(n_windows)/2)

non_seg_dur <- seg_df %>% 
  filter(segmented == F) %>% 
  group_by(Diagnosis_only, visit, id_full) %>% 
  summarize(n_windows = n()) %>% 
  group_by(Diagnosis_only, visit) %>% 
  summarize(mean_duration_total = mean(n_windows)/2, sd_duration_total = sd(n_windows)/2)

seg_dur %>% merge(non_seg_dur, by=c("Diagnosis_only", "visit")) %>%
  kbl(digits = 2, col.names = c("Diagnosis",
                           "Visit",
                           "Mean",
                           "SD",
                           "Mean",
                           "SD")) %>%
  kable_classic(full_width = F) %>%
  add_header_above(c(" " = 2, "Participant speech duration" = 2, "Total speech duration" = 2))

## Calculating interview length requires access to the raw data files and is therefore not included in this script.

```

## Figure S1 - Change from visit 1 to 2
### fig s1 a
```{r fig_s1_a}
fig_s1_a <- wdf_30 %>% 
  group_by(id_full, visit, Diagnosis_only) %>% 
  summarise(mean_prob = mean(probs)) %>% 
  group_by(id_full, Diagnosis_only) %>% 
  summarise(dif = diff(mean_prob)) %>% 
  mutate(absolute = abs(dif)) %>% 
  arrange(desc(dif)) %>% 
  ungroup() %>% 
  mutate(id_full = fct_reorder(id_full, dif, .desc=FALSE)) %>% 

  ggplot(aes(id_full, dif, color=Diagnosis_only)) +
    geom_segment(aes(x=id_full, xend=id_full, y=0, yend=dif)) +
    geom_point(size=2) +
    coord_flip(ylim=c(-0.5, 0.5)) +
    scale_color_brewer(palette = "Set1", direction = -1) +
    labs(y="Difference in P(happy)", x="ID") +
    theme(legend.title = element_blank(),
          axis.text.y = element_blank(),
          legend.position = 'right')


```

### fig s1 b
```{r}
cont_heat <- wdf_30 %>% 
  filter(Diagnosis_only == 'Controls') %>% 
  mutate(visit = paste('Visit', visit)) %>% 
  group_by(Diagnosis_only, visit, id_full) %>% 
  # Add column with 'time' based on number of windows
  mutate(consec = sequence(rle(as.character(id_full))$lengths)) %>% 
  ungroup() %>%
  group_by(Diagnosis_only, visit) %>% 
  mutate(id_full = fct_reorder(id_full, probs, .fun = median, .desc=TRUE)) %>% 
  ggplot(aes(consec-1, id_full, fill=probs)) +
  geom_tile() +
  facet_grid(Diagnosis_only ~ visit) +
  #facet_wrap(~Diagnosis_only, scales='free_y') +
  scale_fill_scico(palette = 'lajolla', direction = -1) +
  labs(x = 'Time', fill='P(Happy)') +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        legend.position="right")

dep_heat <- wdf_30 %>% 
  filter(Diagnosis_only == 'Depression') %>% 
  mutate(visit = paste('Visit', visit)) %>% 
  group_by(Diagnosis_only, visit, id_full) %>% 
  # Add column with 'time' based on number of windows
  mutate(consec = sequence(rle(as.character(id_full))$lengths)) %>% 
  ungroup() %>%
  group_by(Diagnosis_only, visit) %>% 
  mutate(id_full = fct_reorder(id_full, probs, .fun = median, .desc=TRUE)) %>% 
  ggplot(aes(consec-1, id_full, fill=probs)) +
  geom_tile() +
  facet_grid(Diagnosis_only ~ visit) +
  #facet_wrap(~Diagnosis_only, scales='free_y') +
  scale_fill_scico(palette = 'lajolla', direction = -1) +
  labs(x = 'Time', fill='P(Happy)') +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")


fig_s1_b <- (dep_heat + theme(legend.position = 'none')) / cont_heat +
  plot_layout(guides = 'collect') & theme(strip.background = element_rect(color = 'grey'))
```

### Figure S1 combined
```{r fig_s1, fig.width=12.5, fig.height=10}

fig_s1_a / fig_s1_b + 
  plot_annotation(tag_levels = list(c("A", "B", "")))

ggsave("supplementary/fig_s1.pdf", dpi="retina", width = 12.5, height = 10)
```


## Figure S2 - Difference in estimated P(Happy) between groups
```{r fig_s2}
plot_and_print_dif <- function(df, col, title=NULL, xlim=NULL){
  if(is.null(title)) title <- col
  p <- df %>% 
    ggplot(aes_string(col))
  if(!is.null(xlim)){
    p <- p +
      xlim(xlim)
  }
  p <- p +
    stat_halfeye() +
    labs(x = "P(Happy)", y = "Density", title = title)
  
  quants <- quantile(df[[col]], c(0.025, 0.5, 0.975))
  return(list(plot=p, quants=quants))
}

# Based on dummy samples
diffs <- samps_raw_mix %>% 
  preprocess_samples() %>% 
  mutate(block = rep(seq(from=1, to=2*n_samples), 4)) %>% # Fix pivoting error (avoid duplicate rows)
  select(-visit) %>% 
  pivot_wider(names_from = key, values_from = value) %>% 
  mutate(diff_dep_cont = Controls1 - Depression,
         diff_dep_rem = Remission - Depression,
         diff_cont_rem = Controls1 - Remission,
         diff_cont = Controls1 - Controls2) 

dummy_dep_cont <- plot_and_print_dif(diffs, "diff_dep_cont", "Controls1 - Depression2")
dummy_dep_rem <- plot_and_print_dif(diffs, "diff_dep_rem", "Depression2 - Depression1")
dummy_cont_rem <- plot_and_print_dif(diffs, "diff_cont_rem", "Controls1 - Depression2")
dummy_cont <- plot_and_print_dif(diffs, "diff_cont", "Controls1 - Controls2")

(dummy_cont_rem$plot + dummy_cont$plot) /
  (dummy_dep_cont$plot + dummy_dep_rem$plot) 

ggsave("supplementary/fig_s2.pdf", dpi="retina", width = 10, height = 8)

tibble(dep_cont = dummy_dep_cont$quants,
       dep_rem = dummy_dep_rem$quants,
       cont_rem = dummy_cont_rem$quants,
       cont = dummy_cont$quants) %>% 
  t(.) %>% 
  as.data.frame() %>% 
  kbl(digits=3,
      format="html",
      row.names = T, 
      col.names = c("2.5%", "Median", "97.5%")) %>% 
  kable_classic(full_width=F)
```

## Figure S3 - BEST
### BEST - functions
```{r best_functions}
# BEST t-test (Kruschke 2013)
# Code adapted from https://www.andrewheiss.com/blog/2019/01/29/diff-means-half-dozen-ways/#regression-best-with-priors-on-variables-instead-of-difference


run_BEST <- function(df, file){
  # Setting reasonable priors
  priors <- c(set_prior("normal(0, 0.5)", class = "b"), #
              # Setting prior for nu to 1/29 in line with BEST paper
              set_prior("exponential(1.0/29)", class = "nu"))
  
  best_brms <- brm(bf(probs ~ 0 + Diagnosis_only + (1|gr(id_full, by=Diagnosis_only)), 
                      # assessing the effect of diagnosis on probs (no intercept)
                      sigma ~ 0 + Diagnosis_only + (1|gr(id_full, by=Diagnosis_only))), 
                      # assessing the whether there is a difference in sigmas by diagnosis
                   prior = priors,
                   data=df, 
                   family=student,
                   chains=4,
                   iter=6000,
                   warmup=2000,
                   seed=60,
                   file = file)
}

# Calculate difference in group means.
# Extract posterior samples from each group, subtract them, 
# calculate CI
calc_post_diff_means <- function(brms_model) {
  
  groups_post <- posterior_samples(brms_model) %>% 
    # Exponentiating sigma
    mutate_at(vars(contains("sigma")), funs(exp)) %>% 
    # Need to log nu
    mutate(nu = log10(nu)) %>% 
    mutate(diff_means = b_Diagnosis_onlyControls - b_Diagnosis_onlyDepression,
           diff_sigma = 
             b_sigma_Diagnosis_onlyControls - b_sigma_Diagnosis_onlyDepression) %>% 
    # Calculate effect size (Cohen's d and common language ES)
    mutate(cohen_d = diff_means / 
             sqrt((b_sigma_Diagnosis_onlyControls + b_sigma_Diagnosis_onlyDepression)/2),
           cles = dnorm(diff_means / sqrt((b_sigma_Diagnosis_onlyControls + b_sigma_Diagnosis_onlyDepression)), 0, 1))
  
  return(groups_post)
}

# Tidy output and calculate 95% HDI
tidy_post_means <- function(groups_post) {
  
  groups_post_tidy <- groups_post %>% 
    tidyMCMC(conf.int = TRUE, conf.level = 0.95, 
             estimate.method = "median", conf.method = "HPDinterval")
  return(groups_post_tidy)
}

# Identify columns of interest
get_keep_cols <- function(tidy_post_means) {
  keep_cols <- bind_rows(head(tidy_post_means, 4), 
                         tail(tidy_post_means, 4)) %>% 
    pull(term)
  return(keep_cols)
  
}
```
### BEST - run models
```{r best_run_models}
# Setting up dataframes
clean_v1 <- wdf_30 %>% 
  filter(visit == 1)

raw_v1 <- df %>% 
  filter(visit == 1, clean == 'raw', window_size == '30')

non_seg <- seg_df %>% 
  filter(visit == 1, segmented == F)

# Parallel processing
options(mc.cores = parallel::detectCores())

dfs <- list(Diarized = clean_v1, Raw = raw_v1, `Not diarized` = non_seg)
brms_files <- c(here("models", 'best_brms'), here("models", 'raw_brms'), here("models", 'non_seg_brms'))

# Train/load BEST model on each dataset
models <- dfs %>% map2(brms_files, run_BEST)
```
### BEST - plot (figure S3)
```{r fig_s3}
# Extract posterior samples and calculate difference in means
groups_post <- map(models, calc_post_diff_means)
# Get tidy output posterior samples
groups_post_tidy <- map(groups_post, tidy_post_means)
# Extract names of the columns to plot
keep_cols <- get_keep_cols(groups_post_tidy$Diarized)

# Plot
main_post_plot <- groups_post %>% 
  bind_rows(.id = "Dataset") %>% 
  select(all_of(keep_cols), Dataset, -c(cles, cohen_d)) %>% 
  pivot_longer(cols = c(everything(), -Dataset)) %>% 
  mutate(name = str_remove(name, "Diagnosis_only"),
         Dataset = fct_rev(Dataset)) %>% 
  filter(!(name %in% c("diff_means", "diff_sigma"))) %>% 
  mutate(name = case_when(name == "b_Controls" ~ "\u03bc Controls",
                          name == "b_Depression" ~ "\u03bc Depression",
                          name == "b_sigma_Depression" ~ "\u03C3 Depression",
                          name == "b_sigma_Controls" ~ "\u03C3 Controls")
         ) %>% 
  ggplot(aes(x=value, y=fct_rev(name), 
             color = Dataset, fill = Dataset)) +
  stat_halfeye(.width = c(0.66, 0.95), alpha = 0.5) +
  #scale_y_discrete(labels = c("b_Controls" = expression(mu, "Controls"))) %>% 
  scale_fill_brewer(palette = 'Dark2', direction = -1) +
  scale_color_brewer(palette = 'Dark2', direction = -1) +
  labs(x = "P(Happy)") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.title.y = element_blank()) 


cohen_d_plot <- groups_post %>% 
  bind_rows(.id = "Dataset") %>% 
  select(cohen_d, Dataset) %>% 
  pivot_longer(cols = c(everything(), -Dataset)) %>% 
  mutate(name = str_remove(name, "Diagnosis_only"),
         Dataset = fct_rev(Dataset)) %>% 
  mutate(name = ifelse(name == "cohen_d", "Cohen's d")) %>% 
  ggplot(aes(x=value, y=fct_rev(name), 
             color = Dataset, fill = Dataset)) +
  stat_halfeye(.width = c(0.66, 0.95), alpha = 0.5) +
  scale_fill_brewer(palette = 'Dark2', direction = -1) +
  scale_color_brewer(palette = 'Dark2', direction = -1) +
  labs(x = "Cohen's d") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.title.y = element_blank())

# figure s3
main_post_plot / cohen_d_plot +
  plot_layout(guides = "collect", heights = unit(c(10, 1), c('cm'))) & 
  theme(legend.position = 'bottom')

ggsave("supplementary/fig_s3.pdf", dpi="retina", width = 10, height = 8, device = cairo_pdf)
```


## Table S2 - AUC on preprocessed data
```{r}
clean_auc <- get_auc(df, "clean")
raw_auc <- get_auc(df, "raw")
seg_auc <- get_auc(seg_df, "null", T)

bind_rows(clean_auc, raw_auc, seg_auc) %>% 
  relocate(Data) %>% 
  arrange(Type, desc(AUC)) %>% 
  select(-Type) %>% 
  mutate(Data= recode(Data, clean = "Diarized", raw = "Raw", seg = "Not diarized")) %>% 
  kbl() %>% 
  kable_classic(full_width = F) %>% 
  pack_rows("Summary", 1, 3) %>% 
  pack_rows("Windows", 4, 6)
```

## Table S3 - Tabular BEST
```{r table_s3}
groups_post %>%
  bind_rows(.id = "Dataset") %>%
  select(all_of(keep_cols), Dataset, -c(cles)) %>%
  pivot_longer(cols = c(everything(), -Dataset)) %>%
  mutate(name = str_remove(name, "Diagnosis_only"),
         Dataset = fct_rev(Dataset)) %>%
  mutate(name = case_when(name == "b_Controls" ~ "\u03bc Controls",
                          name == "b_Depression" ~ "\u03bc Depression",
                          name == "b_sigma_Depression" ~ "\u03C3 Depression",
                          name == "b_sigma_Controls" ~ "\u03C3 Controls",
                          TRUE ~ name)
  ) %>%
  group_by(name, Dataset) %>%
  mean_qi(value) %>%
  ungroup() %>%
  select(Dataset, value, .lower, .upper) %>%
  kbl(digits=2) %>%
  kable_classic(full_width = F) %>%
  pack_rows("Cohen's d", 1, 3) %>%
  pack_rows("Diff. means", 4, 6) %>%
  pack_rows("Diff. sigma", 7, 9) %>%
  pack_rows("\u03bc Controls", 10, 12) %>%
  pack_rows("\u03bc Depression", 13, 15) %>%
  pack_rows("\u03C3 Controls", 16, 18) %>%
  pack_rows("\u03C3 Depression", 19, 21)

  
```


## Figure S4 - Prognosis
### fig s4 a
```{r}
### For model building see `model.Rmd` 
# Finding those in remission
remission_ids <- wdf_full %>% 
  filter(Diagnosis_only == "Depression") %>% 
  group_by(id_full) %>% 
  summarise(n = n()) %>%
  filter(n == 2) %>% 
  pull(id_full)

dep_30 <- wdf_30 %>% 
  select(log_odds, id_full, Diagnosis_only, visit, probs) %>% 
  filter(Diagnosis_only == "Depression", visit == 1) %>% 
  mutate(Remission = if_else(id_full %in% remission_ids, 1, 0)) 

brms_prognosis <- readRDS(here("models", "prognosis.Rds"))

rem_post <- posterior_samples(brms_prognosis)

dep <- rem_post$b_Intercept
rem <- rem_post$b_Intercept + 
  rem_post$b_Remission

fig_s4a <- tibble(diff = dep - rem) %>% plot_and_print_dif("diff", "")
```

### fig s4 b
```{r}
fig_s4b <- dep_30 %>% 
  mutate(Remission = if_else(Remission == 0, "No remission", "Remission")) %>% 
  group_by(Remission, id_full) %>% 
  summarise(probs = mean(probs)) %>%
  group_by(Remission) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  mutate(Remission = paste0(Remission,'\nN = ',n)) %>% 
  ggplot(aes(Remission, probs, fill=Remission, color=Remission)) +
  geom_point(alpha=0.5, position = position_jitterdodge(jitter.width = 0.1)) +
  geom_boxplot(aes(group=Remission), alpha=0.3, width = 0.5, color='black') +
  ylim(0,1) +
  theme(legend.position = 'none',
        axis.title.x = element_blank()) +
  scale_color_manual(values=c(rem_pal[2], rem_pal[4])) +
  scale_fill_manual(values=c(rem_pal[2], rem_pal[4])) +
  labs(y = "P(Happy)")
```

### Figure S4 combined
```{r fig_s4}
layout <- "
AAA
AAA
BBB
BBB
BBB
BBB"
fig_s4a$plot / fig_s4b + 
  plot_annotation(tag_levels = "A") +
  plot_layout(design = layout)

ggsave("supplementary/fig_s4.pdf", dpi="retina", width = 10, height = 8)
```


## Figure S5- Std of P(Happy) by participant
```{r fig_s5}
# Sds by participant
wdf_30 %>% 
  group_by(Diagnosis_rem, id_full) %>% 
  summarize(sd_probs = sd(probs)) %>% 
  ggplot(aes(x=sd_probs, y=Diagnosis_rem, fill=Diagnosis_rem)) +
  geom_point() +
  stat_halfeye(.width=0, slab_alpha=0.5, aes(color=Diagnosis_rem)) +
  scale_fill_manual(values=rem_pal) +
  scale_color_manual(values=alpha(rem_pal, 0.2)) +
  theme(legend.position = "none",
        axis.title.y = element_blank()) +
  labs(x = "Std of P(Happy)")

ggsave("supplementary/fig_s5.pdf", dpi="retina", width = 10, height = 8)
```


## Table S4 Tabular std of P(happy) by group
```{r}
wdf_30 %>% 
  group_by(Diagnosis_visit, id_full) %>% 
  summarize(sd_probs = sd(probs)) %>% 
  group_by(Diagnosis_visit) %>% 
  summarize(m = mean(sd_probs), s = sd(sd_probs)) %>% 
  kbl(digits=3, col.names = c("Diagnosis", "Mean std P(Happy)", "Std of mean std P(Happy")) %>% 
  kable_classic(full_width=F)
```


## Figure S6 - Prior and posterior predictive checks
```{r fig_s6}
mix_m_prior <- readRDS(here("models", "mixture_model_prior_only.rds"))

pp_prior <- brms::pp_check(mix_m_prior, nsamples=100)
pp_post <- brms::pp_check(mix_m, nsamples=100)

pp_prior / pp_post + plot_annotation(tag_level="A")

ggsave("supplementary/fig_s6.pdf", dpi="retina", width = 10, height = 8)
```

## Figure S7 - Posterior updates
```{r fig_s7}
posterior_samples(mix_m) %>% 
  select(starts_with("prior"), starts_with("b_"), starts_with("sigma")) %>% 
  mutate(`prior_b_theta1_visit0:Diagnosis_onlyControls` = prior_b_theta1,
         `prior_b_theta1_visit1:Diagnosis_onlyControls` = prior_b_theta1,
         `prior_b_theta1_visit0:Diagnosis_onlyDepression` = prior_b_theta1) %>% 
  rename(prior_mu1_Intercept = prior_Intercept_mu1,
         prior_mu2_Intercept = prior_Intercept_mu2,
         `prior_b_theta1_visit1:Diagnosis_onlyDepression` = prior_b_theta1) %>% 
  select(-c(prior_cor_id_full_1, prior_cor_id_full_2, prior_sd_id_full)) %>% 
  gather() %>% 
  mutate(is_prior = if_else(substr(key, 1, 5) == "prior", "Prior", "Posterior"),
         key = if_else(substr(key, 1, 5) == "prior", 
                       substr(key, 7, 100),
                       key),
         key = if_else(substr(key, 1, 1) == "b",
                       substr(key, 3, 100),
                       key),
         key = str_remove(key, "Diagnosis_only")
  )  %>% 
  
  ggplot(aes(value, fill = is_prior)) +
  geom_density(alpha=0.3) +
  facet_wrap(~key, scale="free") + 
  scale_fill_brewer(palette = "Pastel1") +
  labs(x = "Log odds") + 
  theme(legend.position = "bottom",
        legend.title = element_blank())

ggsave("supplementary/fig_s7.pdf", dpi="retina", width = 10, height = 8)
```

## Figure S8 - Delta hamilton as a function of delta P(Happy)
```{r}
###### 
#This requires a dataset with more data on the participants and can therefore not be directly reproduced
######

# remission_ids <- wdf_full %>% 
#   filter(Diagnosis_only == "Depression") %>% 
#   group_by(id_full) %>% 
#   summarise(n = n()) %>%
#   filter(n == 2) %>% 
#   pull(id_full)
# 
# wdf_30 %>% 
#   select(probs, id_full, Diagnosis_only, visit, probs, HamD17_Before, HamD17_After) %>% 
#   filter(Diagnosis_only == "Depression") %>% 
#   group_by(id_full, visit) %>% 
#   summarise(ham_before = mean(HamD17_Before), ham_after = mean(HamD17_After),
#             probs = mean(probs)) %>%  
#   group_by(id_full) %>% 
#   summarise(d_probs = diff(probs), d_ham = ham_before - ham_after) %>% 
#   distinct() %>% 
#   ggplot(aes(x=d_ham, y=d_probs)) +
#   geom_point() +
#   labs(y = "\u0394 P(Happy)", x = "\u0394 HamD-17")
# 
# ggsave("supplementary/fig_s8.tiff", dpi="retina", width = 10, height = 8)





```



## Package citations
```{r}
pat <- "package:(.*)"
packages <- sub(pat, "\\1", grep(pat, search(), value = TRUE))
cite_packages <- c("base", packages[-(which(packages == "stats"):length(packages))]) #Adds base R citation and removes base packages

capture.output(
	for (i in cite_packages) print(citation(i), style = "BibTeX"),
	file = "R_cite.bib")
```

